%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparwidth=.7in}
\setlength\parindent{0in}

% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setromanfont [Ligatures={Common}, BoldFont={Gentium Basic Bold}, ItalicFont={Gentium Basic Italic}]{Gentium Basic}
\setmonofont[Scale=0.8]{Monaco} 
% ---- CUSTOM AMPERSAND
%\newcommand{\amper}{{\fontspec[Scale=.95]{Gentium Basic Italic}\selectfont\itshape\&}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\footnotesize #1}}
\newcommand{\mnote}[1]{\years{\normalsize #1}}
\renewcommand*{\raggedleftmarginnote}{\raggedleft}
\setlength{\marginparsep}{10pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\upshape\Large}
\subsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\subsubsectionfont{\rmfamily\mdseries\upshape\normalsize} 

% PDF SETUP
\usepackage[ bookmarks, colorlinks, breaklinks
           , pdftitle={Evgeny Zakrevsky CV}
           , pdfauthor={Evgeny Zakrevsky}
           ]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 

% DOCUMENT
\begin{document}

{\LARGE Evgeny Zakrevsky}\\[1em]

\years{\normalsize Address:} Nevsky prosp. 126-76\\
 Saint Petersburg, 191036, Russia \\[.2cm]
\years{\normalsize Born:}  December 14, 1989 — Siverskii, USSR\\[.2cm]
\years{\normalsize Phone:} \texttt{+7 (909) 587-87-11}\\[.2cm]
\years{\normalsize Email:} \href{mailto:zakrevsky.evgeny@gmail.com}{zakrevsky.evgeny@gmail.com}\\[.4cm]
\years{\normalsize Skype:} zakrevsky.evgeny\\[.4cm]
% \vfill

%%%%%%%%%%%%%%%%%%%%
\section*{Education}

\years{2007–2012}Saint Petersburg State University, Faculty of Mathematics and Mechanics, Specialist degree in Applied Mathematics. \\
Diploma thesis: ``Limit cycles in Lienard system'';\\
\years{2005–2007}Academic Gymnasium at Saint Petersburg State University; \\
\years{1997–2005}Tosno's school n.1 with improved study of particular subjects, Tosno, Leningrad Region.\\[.4cm]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Additional education}

\years{2009–2010}Practice at Motorola corp. (2 semesters) — Developed programs for testing (Java, Eclipse, JUnit, XML, Swing); \\
\years{2009–2010}Special course of business programming by Exigen Services company (2 semesters) — JavaEE lessons; \\
\years{2007–2008}Participation in the programming contests (2 semesters) at Saint Petersburg State University; \\
\years{2000–2005}Attended introductory programming courses (5 years).\\[.4cm]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Awards \& achievements}
%\subsection*{In the discipline of Mathematics}

\years{2008}Participation in the 1/4 ACM ICPC;\\
\years{2002}First prize at regional tour of the International Mathematical Kangaroo Olympiad;\\
\years{2005}First prize at first tour of the Russian Mathematical Olympiad.\\[.4cm]

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Work experience}

\years{2011–2012}JetBrains. IntelliJ IDEA team. User interface design; task management and time tracking plugins (Java, Swing, REST API, Git);\\
\years{2010–2010}SmartKupon. Developed back-office for a mobile marketing system from scratch (Java, JavaEE, Spring-IoC, Tomcat, MySQL, HTML, CSS, Apache Ant, Subversion).\\[.4cm]

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Side projects}

\years{2011}CodePad. Test task at JetBrains. Objective C code editor for iPad with large files support (Objective C, XCode).\\[.4cm]

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Computer skills}

\subsection*{Proficient user of}
Mac OS X, Windows operating systems; Maple computer algebra system; IntelliJ IDEA IDE.

\subsection*{Programming experience (in descending order)}
Java, Objective C.

%%%%%%%%%%%%%%%%%%%%
%\section*{Languages}

%{\it Russian:} native speaker;\\
%{\it English:} IELTS band score 7.0 (June 2012).

\vfill{}

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
\fontspec{Times New Roman}\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
%Source: \href{https://github.com/zakrevsky/cvtex}{https://github.com/zakrevsky/cvtex}
}
\end{center}

\end{document}
